%% Cover Letter by Yasin Tosun
%% CoursEcon / 2nd National Summer Seminars
%% Genç Ekonomistler Kulübü / 22.08.2022
%% Copyright 2021 - 2028 / Yasin Tosun 
%% Info: courseconomics@gmail.com
%----------------------------------------------------------------------%
%% Paper / Document Details
\documentclass[10pt,a4paper]{article} 
	% Possible options include;
	% 	font size ('10pt', '11pt' and '12pt'), 
	% 	paper size ('letterpaper','legalpaper','executivepaper','landscape') 
	% 	font family ('sans' and 'roman')
%----------------------------------------------------------------------%
%% Write Language
\usepackage[turkish]{babel}
%----------------------------------------------------------------------%
%% Character Encoding
\usepackage[latin5]{inputenc}
\usepackage[T1]{fontenc}
%----------------------------------------------------------------------%
%% Page Margins
\usepackage[top=2.00cm]{geometry}
%----------------------------------------------------------------------%
%% Gap Code
\usepackage{setspace}
%----------------------------------------------------------------------%
%% Determining line spacing
\setlength{\parskip}{0,2cm}
%----------------------------------------------------------------------%
%% Color Pattern
\usepackage{xcolor}
%----------------------------------------------------------------------%
%----------------------------------------------------------------------%

\begin{document}	

	%% Page Numbers/Non-Numbers
	\thispagestyle{empty}

	%% Line Gap
    \onehalfspacing
  
	\begin{quote}
	%% Date
	\hfill \textbf{August 19, 1945}\newline
	% {\today}
	\end{quote}                              	

	\begin{flushleft}
	%% Major Title
	\textcolor{black}{\LARGE\textbf{Cover Letter}} \newline
	
	%% Minor Title	
	\textcolor{violet}{\textit{{\large {Doctorate Application of  Columbia University / $ 38^{th} $ Cycle}}}}
	%\opening{Dear Sir $ & $ Madam}
	%\opening{Dear Professor}
	%\opening{To whom it May concern}
	% Daha fazla renk için "LaTeX:Using Color" þeklinde arama yapabilirsiniz.

	%Gap 
	\vspace{0.5cm}
	
	%% Setting The Line Start Indent
	\setlength{\parindent}{0,3cm}	

	Dear Professor,
	
	I am Milton Friedman , after completing my Master's degree at Chicago University, I have been working as a research assistant at the NBER since 1937. I research on consumption analysis, monetary history and theory and the complexity of stabilization policy. When I see your ad, I think I will take myself to a higher level, especially in macroeconomics and monetary policy. 
	
	\setlength{\parindent}{0,3cm}
	One of the reasons for my application is the reason why I decided to have courses in my field of study. I also believe that I can demonstrate my abilities in the advancement of economic policy with econometrics. In addition to theory, I think I will improve my field skills with econometric applications. In addition, he is excited by the fact that he is educated at a very good university, has a wide network and job opportunities. In addition, I believe that having a rich academic staff with multiple interdisciplinary studies will further deepen my perspective and equipment on established economics. This opportunity makes me even more happy as I have been the assistant of many academicians in different field courses. Also, since I work as a research assistant at the NBER, I think that I will adapt quickly and quickly with my experience in many assistantships and organization.
	
	\setlength{\parindent}{0,3cm}
	Thank you for providing ample opportunities by running this program after the economic crisis. When you examine my detailed CV during the evaluation process, I hope that you will be pleased with my academically diverse and qualified education. With all the successes and failures I have experienced, I would be very happy and honored to participate in your program to take a new step and try to improve myself with another challenge. \newline 

	Yours sincerely,
	
	
	\vspace{0.5cm}
	
	\textbf{Milton Friedman}
	
	\vspace{0.1cm}
	%% Signature
	\textcolor{olive}{\textit{"There is no such thing as a Free Lunch"}}
	
	 
	\end{flushleft}

\end{document}